---
title: "Rmd Exercise Template"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The question you are answering

You use the `##` to create a header. Use the header to indicate the question you are answering. After the header, in this space here, annotate your answer, telling us what you did.

```{r chunk name}
# Here is where your R code goes. ``` opens the code chunk, followed by {r}. Then ``` closes the chunk. When you 'knit' the file, the codes will evaluate.

dat <- read.csv("path/to/data/data.csv")
```

## Including Plots

You can also embed plots, for example:

```{r another chunk name}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

# Load the Data
```{r}
gapminder <- read.csv(here::here("data/gapminder5.csv"), stringsAsFactors=FALSE)
```

# If Statement
```{r}
year <- 2002
if(any(gapminder$year == year)){
    print("There are records from 2002 in the gapminder dataset")
}else {
    print("There are NO records from 2002 in the gapminder dataset")
}
```

# Loop and If Statement
```{r}
countries <- unique(gapminder$country)
continents <- unique(gapminder$continent)
m <- mean(gapminder$pop, na.rm = T)
for (c in countries){
    if (mean(gapminder$pop[gapminder$country == c]) < m){
        mean_le <- mean(gapminder$lifeExp[gapminder$country == c])
        print(paste(c, " ",mean_le))
    }
}

for (con in continents){
    mean_le <- mean(gapminder$lifeExp[gapminder$continent == con])
    if (mean_le > 70){
        print(paste(con, "Greater than 70."))
    }
    else if (mean_le < 50){
        print(paste(con, "Smaller than 50"))
    }
    else{
        print(paste(con, "Between 50 and 70"))
    }
}

```

# Write Functions
```{r}
f_1 <- function(df){
    for (i in 1:ncol(df)){
        a = colnames(df)[i]
        b = class(df[,i])
        print(paste(a, b))
      
    }
}
f_1(gapminder)

f_2 <- function(vec, med = T){
    mean_vec = mean(vec)
    sd_vec = sd(vec)
    med_vec = median(vec)
    if (med){
        cat("Mean:", mean_vec, "\nStandard Deviation:", sd_vec, "\nMedian:", med_vec)
    }else{
        cat("Mean:", mean_vec, "\nStandard Deviation:", sd_vec)
    }
    
}

f_2(c(1:5))

```

# Analyzing the Relationship
```{r}
log_gdp <- log(gapminder$gdpPercap)
log_le <- log(gapminder$lifeExp)
plot(log_gdp~log_le)

```

